A systematic search for transiting planets using \KT

### 2015-02-12 ms.tex
editing the intro a bit

The photometry from the \KT\ extension of NASA's \kepler\ mission is
afflicted by systematic effects caused by the relative imprecision of the
telescope pointing, and possibly other spacecraft effects.
We present a method for searching these light curves for evidence of
exoplanets by simultaneously fitting for these systematics and the
transit signals of interest.
This method is more computationally expensive than standard search algorithms
but we demonstrate that it can be efficiently implemented and used to
discover transit signals in the existing dataset.
We apply this method to the full Campaign 1 dataset and report a list of XXX
planet candidates transiting YYY stars.
For all planet candidates, we present posterior distributions on the
properties of each system based strictly on the transit observables.
We also present a list of ZZZ candidate eclipsing binary systems.

@@

The \kepler\ Mission (cite something) has been incredibly succesful at
finding periodic transits (eclipses) in the light curves (time-series
photometry) of stars (cite something).
The Mission has demonstrated that it is possible to routinely measure
signals in stellar light curves at the part-in-$10^5$ level.
Results from the primary mission include the detection of planet
transits with depths as small as 12 parts per million \citep{Barclay:2013}.

The noise floor for \kepler\ data is often quoted as 15 parts per million per
six hours of observations \citep{Gilliland:2011}.
Although they generally do not influence the ability to search for transiting
planets, larger systematic (noise shits) exist on different timescales.
One of the most serious of these is spacecraft pointing:
If the detector flat-field is not known \emph{exquisitely}, then
tiny changes to the relative illumination of pixels caused by a star's
motion in the focal plane (or caused by motion of the focal-plane
boresight or orientation relative to the celestial sphere) will lead
to changes in the measured or inferred brightness of the star.

The pointing of \kepler\ was stable at the (LEVEL) level (citation) throughout
the primary mission.
This primary mission came to an end with the failure of a critical
reaction wheel, rendering the spacecraft less able to maintain precise
pointing.
The \KT\ Mission \citep{Howell:2014} is a follow-on to the primary
\kepler\ Mission, observing approximately a dozen fields near the ecliptic
plane, each for 75 days at a time.
Because of the degraded spacecraft orientation systems, the new
\KT\ data will in general exhibit far greater pointing
variations---and far greater pointing-induced variations in
photometry---than the original \kepler\ data.
This makes good data-analysis techniques even more valuable.

@@

Previous projects have developed methods to work with \KT\ data.
\citet{Vanderburg:2014} extract aperture photometry from the pixel data
and decorrelate with image centroid position, producing light curves for each
star that are ``corrected'' for the spacecraft motion.
These data have produced the first confirmed planet found with
\KT\ \citep{Vanderburg:2015}.
\citet{Crossfield:2015} iteratively construct a robust Gaussian Process
model for the photometry as a function of the measured centroids and de-trend
using the mean prediction from that model.
DFM HERE IS WHERE WE (cite Dun AAS and in prep).

In these light-curve processing methodologies,
the authors follow a traditional procedure of ``correcting'' the light curve
as a step that happens \emph{before} the search for transiting planets.
Light curves from the primary \kepler\ mission are typically de-trended to
remove the effects of stellar variability before searching for transiting
planets.
With \KT, application of the traditional methods involves fitting and subtracting measured
effects from the spacecraft pointing variations and stellar variability.
Fit-and-subtract is dangerous:
Small signals, such as planet transits, can be partially absorbed into the
best-fit stellar variability or systematics models, making each individual transit event appear
shallower; that is, the traditional methods are prone to over-fitting.
Because over-fitting will in general reduce the amplitude of true exoplanet signals,
small planets that ought to appear just above any specific signal-to-noise
or depth
threshold could be missed because of the de-trending.

>>>>

The photometry from the \KT\ extension of NASA's \kepler\ mission is
afflicted by systematic effects caused by the relative imprecision of the
telescope pointing and other spacecraft effects.
We present a method for searching these light curves for evidence of
exoplanets by simultaneously fitting for these systematics and the
transit signals of interest.
This method is more computationally expensive than standard search algorithms
but we demonstrate that it can be efficiently implemented and used to robustly
discover transit signals.
We apply this method to the full Campaign 1 dataset and report a list of XXX
planet candidates transiting YYY stars.
For all planet candidates, we present posterior distributions on the
properties of each system based strictly on the transit observables.
We also present a list of ZZZ candidate eclipsing binary systems.

@@

The \kepler\ Mission (cite something) has been incredibly successful at
finding transiting exoplanets in the light curves of stars (cite something).
The Mission has demonstrated that it is possible to routinely measure signals
in stellar light curves at the part-in-$10^5$ level.
Results from the primary mission include the detection of planet transits with
depths as small as 12 parts per million \citep{Barclay:2013}.

The noise floor for \kepler\ data is often quoted as 15 parts per million per
six hours of observations \citep{Gilliland:2011}.
Although they generally do not influence the ability to search for transiting
planets, larger systematic effects exist on different timescales.
One of the most serious of these is spacecraft pointing: If the detector
flat-field is not known \emph{exquisitely}, then tiny changes to the relative
illumination of pixels caused by a star's motion in the focal plane will lead
to changes in the measured or inferred brightness of the star.

The pointing of \kepler\ was stable at the (LEVEL) level (citation) throughout
the primary mission.
This stability came to an end with the failure of a critical reaction wheel.
The \KT\ Mission \citep{Howell:2014} is a follow-on to the primary \kepler\
Mission, observing about a dozen fields near the ecliptic plane, each for
$\sim 75$ days at a time.
Because of the degraded spacecraft orientation systems, the new \KT\ data
exhibit far greater pointing variations---and substantially more
pointing-induced variations in photometry---than the original \kepler\ data.
This makes good data-analysis techniques even more valuable.

@@

Previous projects have developed methods to work with \KT\ data.
\citet{Vanderburg:2014} extract aperture photometry from the pixel data
and decorrelate with image centroid position, producing light curves for each
star that are ``corrected'' for the spacecraft motion.
These data have produced the first confirmed planet found with
\KT\ \citep{Vanderburg:2015}.
Both \citet{Aigrain:2015} and \citet{Crossfield:2015} use a Gaussian Process
model for the measured flux, with pointing measurements as the inputs, and
then ``de-trend'' using the mean prediction from that model.
Other data-driven approaches have been developed and applied to the \Kepler\
data \citep[for example,][]{pdc1, pdc2, arc, dun} but they have yet to be
generalized to be applicable to \KT.

In all of these light-curve processing methodologies, the authors follow a
traditional procedure of ``correcting'' or ``de-trending'' the light curve to
remove systematic and stellar variability as a step that happens \emph{before}
the search for transiting planets.
Fit-and-subtract is dangerous: Small signals, such as planet transits, can be
partially absorbed into the best-fit stellar variability or systematics
models, making each individual transit event appear shallower.
In other words, the traditional methods are prone to over-fitting.
Because over-fitting will in general reduce the amplitude of true exoplanet
signals, small planets that ought to appear just above any specific
signal-to-noise or depth threshold could be missed because of the de-trending.
This becomes especially important as the amplitude of the noise increases.
